---
title: "SAGES, MADCO-PC, & INTUIT GCP Harmonization"
author: "Doug Tommet"
date: '`r Sys.Date()`'
format:
  html:
    toc: true
    self-contained: true
    theme: journal
figures:
  fig-cap-location: top 
execute:
  echo: false
  warning: false
  message: false
keep-md: true
---


```{r}
rm(list = setdiff(ls(), lsf.str())[!(setdiff(ls(), lsf.str()) %in% "params")])
source(here::here("R", "001-Libraries_and_functions.R"))
source(here::here("R", "005-folder_paths_and_options.R"))
```


```{r}
sagesI_inperson_df <-   readRDS(file=path(r_objects_folder, "010_sagesI_inperson_df.rds"))
sagesI_560_df <-        readRDS(file=path(r_objects_folder, "010_sagesI_560_df.rds"))
intuit_df <-            readRDS(file=path(r_objects_folder, "010_intuit_df.rds"))

gcp_study_nested <- readRDS(file=path(r_objects_folder, str_c("070_gcp_study_nested_GCPv2b.rds")))
foo <- gcp_study_nested %>%
  filter(study_name_short %in% c("SAGES", "INTUIT_ACTIVE")) %>%
  pull(response_data)

```

# Cognitive battery

## @tbl-battery: Cognitive tests by mode and study

These are the items used to harmonize INTUIT/MADCO to SAGES.  The Duke studies are listed in one column because since they used the same cognitive battery, the two studies were harmonized at the same time.  

```{r}
#| label: tbl-battery
#| tbl-cap: "Cognitive tests by mode and study"
#| tbl-cap-location: top
 
gcp_items <- readRDS(file=path(r_objects_folder, "010_gcp_items.rds"))
gcp_linking_items <- readRDS(file=path(r_objects_folder, "010_gcp_linking_items.rds")) %>%
  select(item_a, item_b)

gcp_items <- gcp_items %>%
  filter(str_detect(item, "Q")) %>%
  filter(!str_detect(Set, "Not")) %>%
  filter(!str_detect(Set, "DNI")) %>%
  # filter(!str_detect(item, "Q7")) %>%
  left_join(gcp_linking_items, by = c("item" = "item_b")) %>%
  select(item, item_a, item_label, study, domain, Set)

gcp_items_wide <- gcp_items %>%
  mutate(item_new = case_when(!is.na(item_a) ~ item_a,
                              TRUE ~ item),
         x = "X") %>%
  select(item_new, study, x) %>%
  pivot_wider(names_from = study, values_from = x)

gcp_items <- gcp_items_wide %>%
  left_join(gcp_items, by = c("item_new" = "item")) %>%
  select(item_new, item_label, Set, domain, everything()) %>%
  select(-item_a, -study) %>%
  arrange(domain, item_new)

gcp_version <- "GCPv2c"
if (gcp_version == "GCPv1"){
  gcp_alt <- c("GCP-alt-1a", "GCP-alt-2a", "GCP-alt-3a")
}
if (gcp_version == "GCPv2a"){
  gcp_alt <- c("GCP-alt-1b", "GCP-alt-2a", "GCP-alt-3a")
}
if (gcp_version == "GCPv2b"){
  gcp_alt <- c("GCP-alt-1b", "GCP-alt-2b", "GCP-alt-3b")
}
if (gcp_version == "GCPv2c"){
  gcp_alt <- c("GCP-alt-1b", "GCP-alt-2c", "GCP-alt-3b")
}

gcp_items <- gcp_items %>%
  filter(Set %in% c("GCP", gcp_alt)) %>%
  filter(!is.na(SAGES) | !is.na(INTUIT_ACTIVE))

gcp_items %>%
  gt::gt() %>%
  gt::cols_hide(columns = c(item_new, domain, Set, HRS_ADAMS, SAGES_Telephone, SAGESII_Inperson, SAGESII_Telephone, SAGESII_Video, SAGESII_Telephone_validation, SAGESII_Video_validation)) %>%
  gt::cols_align(align = "center") %>%
  gt::tab_row_group(label = "Memory", rows = domain %in% c("mem")) %>%
  gt::tab_row_group(label = "Language", rows = domain %in% c("lan")) %>%
  gt::tab_row_group(label = "Attention/Executive Function", rows = domain %in% c("att", "ef")) %>%
  gt::sub_missing(columns = 3:11, rows = everything(), missing_text = "") %>%
  gt::tab_spanner("Study/Mode", 5:11) %>%
  gt::cols_label(INTUIT_ACTIVE = "Duke studies")
  

```

# Descriptive statistics of cognitive assessment

::: callout-note
@tbl-battery-desc is more inclusive of the cognitive tests used in the assessment than @tbl-battery.  Not all the items in this table were used in the GCP, only those in @tbl-battery were used in the GCP.
:::

```{r}
#| label: tbl-battery-desc
#| tbl-cap: "Descriptive statistics of cognitive battery"
#| tbl-cap-location: top
foo_sages <- foo[[1]] 
foo_duke <- foo[[2]]

foo_duke <- foo_duke %>%
  rename(i208 = i708) %>%
  rename(i210 = i710) %>%
  rename(npb14 = digtsym) %>%
  rename(npb10 = trailsa) %>%
  rename(npb12 = trailsb) %>%
  rename(npb15 = repfor) %>%
  rename(npb16 = repback)

goo <- foo_sages %>%
  bind_rows(foo_duke) %>%
  mutate(study = case_when(study_wave_number==2 ~ "SAGES",
                           TRUE ~ study),
         study = factor(study, levels = c("SAGES", "A", "I"), labels = c("SAGES", "MADCO-PC", "INTUIT"))) %>%
  sjlabelled::var_labels(
    randtig = "Immediate RANDT Gist",
    randtiv = "Immediate RANDT Verbatim",
    randtdg = "Delay RANDT Gist",
    randtdv = "Delay RANDT Verbatim",
    i208    = "Hopkins Verbal Learning Initial (3 Trial Sum)",	
    i210    = "Hopkins Delayed recall",
    hvltdelayrecognition = "Hopkins Delayed recognition",
    i713    = "Wechsler Reproduction Immediate (3 trial sum)",		
    i717    = "Wechsler Reproduction Delay (3 trial sum)",
    i201    = "Visual Search and Attention",
    npb14   = "Digit Symbol",              	
    npb10   = "Trails Making Test Part A", 	
    npb12   = "Trails Making Test Part B",	
    npb15   = "Digit Span Repeat Forwards",
    npb16   = "Digit Span Repeat Backwards",
    i241    = "Boston Naming Test",
    i265    = "Semantic fluency – supermarket",
    i281    = "Letter fluency - FAS",
    )



goo %>%
  filter(study_wave_number==2 | (study_wave_number==7 & visit==0))  %>%
  select(study, randtig, randtiv, randtdg, randtdv, i208, i210, hvltdelayrecognition, 
         i713, i717, i201, 
         npb14, npb10, npb12, 
         npb15, npb16, 
         i241, i265, i281) %>%
  gtsummary::tbl_summary(by = study,
                         type = c(randtig, randtiv, randtdg, randtdv) ~ "continuous",
                         statistic = gtsummary::all_continuous() ~ "{mean} ({sd})",
                         digits = gtsummary::everything() ~ 1,
                         missing = "no"
                         ) %>%
  gtsummary::modify_table_body(
    mutate,
    groupname_col = case_when(variable %in% c("randtig", "randtiv", "randtdg", "randtdv", "i208", "i210", "hvltdelayrecognition") ~ "Verbal Memory",
                              variable %in% c("i713", "i717", "i201") ~ "Visual Memory",
                              variable %in% c("npb14", "npb10", "npb12") ~ "Executive Function",
                              variable %in% c("npb15", "npb16") ~ "Attention/Concentration",
                              variable %in% c("i241", "i265", "i281") ~ "Language",
                              TRUE ~ "unlabeled")
  ) %>%
  gtsummary::as_gt() %>%
  gt::sub_values(
    values = "NA (NA)",
    replacement = ""
  )




```

# GCP Information



## @fig-info: Test Information by mode and study

```{r}
#| label: fig-info
#| fig-cap: "Test Information by study"
#| fig-cap-location: top
gcp_study_nested_v2c <- readRDS(file=path(r_objects_folder, "250_gcp_study_nested_GCPv2c.rds"))

foo <- gcp_study_nested_v2c[["h_obj"]]

foo <- gcp_study_nested_v2c %>%
  mutate(boo = map(h_obj, pluck, "test_info"))

goo <- foo %>%
  select(study_name_short, boo) %>%
  unnest(cols = c(boo))

goo %>%
  filter(study_name_short %in% c("SAGES", "INTUIT_ACTIVE")) %>%
  ggplot(aes(x = theta, y = i, color = study_name_short)) +
    geom_line() +
    scale_y_continuous("Information") +
    scale_x_continuous("GCP") +
    # scale_color_discrete("Study", labels = c(SAGES = "SAGES", INTUIT_ACTIVE = "Duke studies"),
    #                      colors = c("#d95f02", "#7570b3")) +
    scale_color_manual("Study", labels = c(SAGES = "SAGES", INTUIT_ACTIVE = "Duke studies"),
                         values = c(SAGES = "#d95f02", INTUIT_ACTIVE = "#7570b3")) +
    hrbrthemes::theme_ipsum()
ggsave(here::here("Figures", "Duke_harmonization_Item_Information.pdf"), device = cairo_pdf)

```

```{r}
#| results: hide
foo <- read_csv(path(derivedfolder, "gcp_factor_score_v2c.csv"))

foo %>%
  filter(study_name_short %in% c("INTUIT_ACTIVE", "SAGES")) %>%
  group_by(study_name_short) %>%
  summarize(n())

```

```{r}
#| label: fig-sem-plot
#| fig-cap: "Standard error measurement of general cognitive performance in SAGES (n = 5949) and MADCO-PC (n = 250), INTUIT (n = 369) "
#| fig-cap-location: top

foo <- read_csv(path(derivedfolder, "gcp_factor_score_v2c.csv"))

foo %>%
  filter(study_name_short %in% c("INTUIT_ACTIVE", "SAGES")) %>%
  mutate(gcp_se = g_se*10) %>%
  group_by(study_name_short) %>%
  ggplot(aes(x = gcp, y=gcp_se, color = study_name_short)) +
    geom_hline(yintercept = 3.16) +
    geom_smooth(se=FALSE) +
    geom_rug(sides="b", alpha=.2) +
    hrbrthemes::theme_ipsum() +
    scale_x_continuous("GCP") +
    scale_y_continuous("GCP Standard Error", lim = c(0, 8)) +
    scale_color_manual("Study", values = c(SAGES = "#d95f02", INTUIT_ACTIVE = "#7570b3")) +
    theme(legend.position="none") +
    annotate("text", 75, 2, label = "SAGES", color = "#d95f02") +
    annotate("text", 75, 4, label = "MADCO-PC & INTUIT", color = "#7570b3")
ggsave(here::here("Figures", "Duke_harmonization_SEM.pdf"), device = cairo_pdf)


foo %>%
  filter(study_name_short %in% c("INTUIT_ACTIVE", "SAGES")) %>%
  mutate(gcp_se = g_se*10) %>%
  group_by(study_name_short) %>%
  ggplot(aes(x = gcp, y=gcp_se, color = study_name_short)) +
    geom_hline(yintercept = 3.16) +
    geom_point(alpha = .10, size = .5) +
    geom_smooth(se=FALSE) +
    scale_x_continuous("GCP") +
    scale_y_continuous("GCP Standard Error", lim = c(0, 8)) +
    scale_color_manual("Study", values = c(SAGES = "#d95f02", INTUIT_ACTIVE = "#7570b3"),
                       labels = c(SAGES = "SAGES", INTUIT_ACTIVE = "MADCO-PC & INTUIT")) +
    hrbrthemes::theme_ipsum()
ggsave(here::here("Figures", "Duke_harmonization_SEM2.pdf"), device = cairo_pdf)

```

## GCP vs CCI in Duke studies

```{r}

intuit_cci_df <- read_xlsx(fs::path(sages_datapath, "SOURCE", "INTUIT", "MADCOPC_INTUIT_DukeCCI.xlsx"))
intuit_gcp <- read_csv(path(derivedfolder, "intuit_gcp.csv"))
sagesI_gcp <- read_csv(path(derivedfolder, "sagesI_gcp.csv"))

foo <- intuit_cci_df %>%
  left_join(intuit_gcp, by = c("studyno" = "newid", "visit" = "timefr"))

foo %>%
  ggplot(aes(x = gcp, y = Duke_CCI)) +
    geom_point() +
    geom_smooth(se = FALSE) +
    hrbrthemes::theme_ipsum()

ggsave(here::here("Figures", "Duke_harmonization_GCP_CCI.pdf"), device = cairo_pdf)
```

