---
title: "Comparison of GCP versions"
output: powerpoint_presentation
author: "Doug Tommet"
date: '`r Sys.Date()`'
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source(here::here("R", "001-Libraries_and_functions.R"))
source(here::here("R", "005-Folder_paths_and_options.R"))

```

```{r}
item_bank_v1 <- read_csv(here("data", "gcp_item_bank_v1.csv"))
item_bank_v2a <- read_csv(here("data", "gcp_item_bank_v2a.csv"))
item_bank_v2b <- read_csv(here("data", "gcp_item_bank_v2b.csv"))
item_bank_v2c <- read_csv(here("data", "gcp_item_bank_v2c.csv"))

gcp_study_nested_v2b <- readRDS(file=path(r_objects_folder, "070_gcp_study_nested_GCPv2b.rds"))
sagesI_npb <- gcp_study_nested_v2b[["response_data"]][[2]] %>%
  select(newid, i201, i208, i210, i241, i265, i282, i283, i284, npb10, npb12, npb14, npb15, npb16)

if(fs::dir_exists(sagesI_datafolder)) {
  sagesI_df <- read_dta(fs::path(sagesI_datafolder, "SAGES-Subject-Interview-Data-Analysis-File.dta"))
  saveRDS(sagesI_df,  file=path(r_objects_folder, "xxx_sagesI_df.rds"))
} else {
  sagesI_df <- readRDS(file=path(r_objects_folder, "xxx_sagesI_df.rds"))
}
  
sagesI_gcp <- sagesI_df %>%
  filter(timefr==0) %>%
  select(studyid, vdgcp)
  # select(studyid, vdgcp, npb01, npb02, npb03, npb17, npb06, npb08, npb10, npb12, npb14, npb15, npb16, npb34, npb25, npb28, npb31, npb37, npb38, npb39)
  
gcp_g_v1 <- read_csv(path(derivedfolder, "gcp_factor_score_v1.csv"))
gcp_g_v2a <- read_csv(path(derivedfolder, "gcp_factor_score_v2a.csv"))
gcp_g_v2b <- read_csv(path(derivedfolder, "gcp_factor_score_v2b.csv"))
gcp_g_v2c <- read_csv(path(derivedfolder, "gcp_factor_score_v2c.csv"))

gcp_g_v1 <- gcp_g_v1 %>% 
  mutate(g = g * 10 + 50,
         g_se = g_se * 10) %>%
  rename(GCP_v1 = g) %>%
  rename(g_se_v1 = g_se)
gcp_g_v2a <- gcp_g_v2a %>% 
  mutate(g = g * 10 + 50,
         g_se = g_se * 10) %>%
  rename(GCP_v2a = g) %>%
  rename(g_se_v2a = g_se)
gcp_g_v2b <- gcp_g_v2b %>% 
  mutate(g = g * 10 + 50,
         g_se = g_se * 10) %>%
  rename(GCP_v2b = g) %>%
  rename(g_se_v2b = g_se)
gcp_g_v2c <- gcp_g_v2c %>% 
  mutate(g = g * 10 + 50,
         g_se = g_se * 10) %>%
  rename(GCP_v2c = g) %>%
  rename(g_se_v2c = g_se)

gcp_g <- gcp_g_v1 %>%
  left_join(gcp_g_v2a, by = c("newid", "study_name_short", "study_wave_number")) %>%
  left_join(gcp_g_v2b, by = c("newid", "study_name_short", "study_wave_number")) %>%
  left_join(gcp_g_v2c, by = c("newid", "study_name_short", "study_wave_number"))
  
sagesI_gcp <- gcp_g %>%  
  left_join(sagesI_gcp, by = c("newid" = "studyid")) %>%
  filter(study_wave_number == 2)
```

# Intro

When we first made the GCP, we made some mistakes and had questionable assumptions.

Now with this harmonization work we have a chance to revisit and possibly correct these mistakes and assumptions.

------------------------------------------------------------------------

# Mistakes

-   GCP v 1.0 (Gross et al 2014, and as used in SAGES encoded in VDS) has a few minor errors and questionable decisions.
-   [Error \#1, \#2, \#3 & \#4]{.ul}. Top two categories (based on quantiles) in VSAT, HVLT, HVLT delayed, and Digit Symbol Substitution are collapsed. This was unintentional, the data would have supported more categories.
-   The result of this is we may not have as precise a measure of cognitive performance among the very top (best) performers.

------------------------------------------------------------------------

# Questionable assumptions

-   [Questionable assumption \#1]{.ul}. We decided to treat HRS/ADAMS "C, F, and L" letter fluency as equivalent to SAGES "F, A, S" fluency. If this assumption of equivalence is a bad assumption, our linkage to HRS/ADAMS is biased.
-   [Questionable assumption \#2]{.ul}. We decided to treat HRS/ADAMS animal fluency as equivalent to SAGES supermarket. If this assumption of equivalence is a bad assumption, our linkage to HRS/ADAMS is biased.

------------------------------------------------------------------------

# Also...

-   The computational procedures we are using to generate the item bank and linked GCP scores is different now than in GCP 1.0
-   Therefore, the new GCP won't be [exactly]{.ul} the same as GCP 1.0.
-   But these procedural differences are expected to produce trivial differences in scores

------------------------------------------------------------------------

# So we have several options to redo the GCP

-   Retain the mistakes and questionable assumptions (GCP_v1)
-   Fix the mistakes but retain the animal/supermarket and CFL/FAS linking (GCP_v2a)
-   Fix the mistakes and separate linking for animal/supermarket and separate items for C/F/L and F/A/S (GCP_v2b)
-   Fix the mistakes and separate linking for animal/supermarket and separate linking for CLF/FAS (GCP_v2c)

------------------------------------------------------------------------

# Fixing the item recoding mistakes

VSAT: Comparison of parameter estimates

```{r}
item_bank_v1 %>%
  filter(item=="Q222") %>%
  filter(parameter_type == "factor_loading") %>%
  select(parameter_T, estimate.stdyx) %>%
  flextable::flextable() %>%
  flextable::add_header_row(colwidths = c(2), 
                            values = c("Version 1: Factor loading")) %>%
  flextable::set_header_labels(parameter_T = "Parameter",
                               estimate.stdyx = "Std. Estimate")

item_bank_v1 %>%
  filter(item=="Q222") %>%
  filter(parameter_type == "threshold") %>%
  select(parameter_T, estimate.stdyx) %>%
  flextable::flextable() %>%
  flextable::add_header_row(colwidths = c(2), 
                            values = c("Version 1: Thresholds")) %>%
  flextable::set_header_labels(parameter_T = "Parameter",
                               estimate.stdyx = "Std. Estimate")

item_bank_v2a %>%
  filter(item=="Q225") %>%
  filter(parameter_type == "factor_loading") %>%
  select(parameter_T, estimate.stdyx) %>%
  flextable::flextable() %>%
  flextable::add_header_row(colwidths = c(2), 
                            values = c("Version 2a: Factor loading")) %>%
  flextable::set_header_labels(parameter_T = "Parameter",
                               estimate.stdyx = "Std. Estimate")

item_bank_v2a %>%
  filter(item=="Q225") %>%
  filter(parameter_type == "threshold") %>%
  select(parameter_T, estimate.stdyx) %>%
  flextable::flextable() %>%
  flextable::add_header_row(colwidths = c(2), 
                            values = c("Version 2a: Thresholds")) %>%
  flextable::set_header_labels(parameter_T = "Parameter",
                               estimate.stdyx = "Std. Estimate")
```

------------------------------------------------------------------------

# Fixing the item recoding mistakes

HVLT: Comparison of parameter estimates

```{r}
item_bank_v1 %>%
  filter(item=="Q223") %>%
  filter(parameter_type == "factor_loading") %>%
  select(parameter_T, estimate.stdyx) %>%
  flextable::flextable() %>%
  flextable::add_header_row(colwidths = c(2), 
                            values = c("Version 1: Factor loading")) %>%
  flextable::set_header_labels(parameter_T = "Parameter",
                               estimate.stdyx = "Std. Estimate")

item_bank_v1 %>%
  filter(item=="Q223") %>%
  filter(parameter_type == "threshold") %>%
  select(parameter_T, estimate.stdyx) %>%
  flextable::flextable() %>%
  flextable::add_header_row(colwidths = c(2), 
                            values = c("Version 1: Thresholds")) %>%
  flextable::set_header_labels(parameter_T = "Parameter",
                               estimate.stdyx = "Std. Estimate")

item_bank_v2a %>%
  filter(item=="Q226") %>%
  filter(parameter_type == "factor_loading") %>%
  select(parameter_T, estimate.stdyx) %>%
  flextable::flextable() %>%
  flextable::add_header_row(colwidths = c(2), 
                            values = c("Version 2a: Factor loading")) %>%
  flextable::set_header_labels(parameter_T = "Parameter",
                               estimate.stdyx = "Std. Estimate")

item_bank_v2a %>%
  filter(item=="Q226") %>%
  filter(parameter_type == "threshold") %>%
  select(parameter_T, estimate.stdyx) %>%
  flextable::flextable() %>%
  flextable::add_header_row(colwidths = c(2), 
                            values = c("Version 2a: Thresholds")) %>%
  flextable::set_header_labels(parameter_T = "Parameter",
                               estimate.stdyx = "Std. Estimate")
```
------------------------------------------------------------------------

# Fixing the item recoding mistakes

HVLT Delayed: Comparison of parameter estimates

```{r}
item_bank_v1 %>%
  filter(item=="Q227") %>%
  filter(parameter_type == "factor_loading") %>%
  select(parameter_T, estimate.stdyx) %>%
  flextable::flextable() %>%
  flextable::add_header_row(colwidths = c(2), 
                            values = c("Version 1: Factor loading")) %>%
  flextable::set_header_labels(parameter_T = "Parameter",
                               estimate.stdyx = "Std. Estimate")

item_bank_v1 %>%
  filter(item=="Q227") %>%
  filter(parameter_type == "threshold") %>%
  select(parameter_T, estimate.stdyx) %>%
  flextable::flextable() %>%
  flextable::add_header_row(colwidths = c(2), 
                            values = c("Version 1: Thresholds")) %>%
  flextable::set_header_labels(parameter_T = "Parameter",
                               estimate.stdyx = "Std. Estimate")

item_bank_v2a %>%
  filter(item=="Q228") %>%
  filter(parameter_type == "factor_loading") %>%
  select(parameter_T, estimate.stdyx) %>%
  flextable::flextable() %>%
  flextable::add_header_row(colwidths = c(2), 
                            values = c("Version 2a: Factor loading")) %>%
  flextable::set_header_labels(parameter_T = "Parameter",
                               estimate.stdyx = "Std. Estimate")

item_bank_v2a %>%
  filter(item=="Q228") %>%
  filter(parameter_type == "threshold") %>%
  select(parameter_T, estimate.stdyx) %>%
  flextable::flextable() %>%
  flextable::add_header_row(colwidths = c(2), 
                            values = c("Version 2a: Thresholds")) %>%
  flextable::set_header_labels(parameter_T = "Parameter",
                               estimate.stdyx = "Std. Estimate")
```

------------------------------------------------------------------------

# Fixing the item recoding mistakes

Digit symbol substitution: Comparison of parameter estimates

```{r}
item_bank_v1 %>%
  filter(item=="Q241") %>%
  filter(parameter_type == "factor_loading") %>%
  select(parameter_T, estimate.stdyx) %>%
  flextable::flextable() %>%
  flextable::add_header_row(colwidths = c(2), 
                            values = c("Version 1: Factor loading")) %>%
  flextable::set_header_labels(parameter_T = "Parameter",
                               estimate.stdyx = "Std. Estimate")

item_bank_v1 %>%
  filter(item=="Q241") %>%
  filter(parameter_type == "threshold") %>%
  select(parameter_T, estimate.stdyx) %>%
  flextable::flextable() %>%
  flextable::add_header_row(colwidths = c(2), 
                            values = c("Version 1: Thresholds")) %>%
  flextable::set_header_labels(parameter_T = "Parameter",
                               estimate.stdyx = "Std. Estimate")

item_bank_v2a %>%
  filter(item=="Q242") %>%
  filter(parameter_type == "factor_loading") %>%
  select(parameter_T, estimate.stdyx) %>%
  flextable::flextable() %>%
  flextable::add_header_row(colwidths = c(2), 
                            values = c("Version 2a: Factor loading")) %>%
  flextable::set_header_labels(parameter_T = "Parameter",
                               estimate.stdyx = "Std. Estimate")

item_bank_v2a %>%
  filter(item=="Q242") %>%
  filter(parameter_type == "threshold") %>%
  select(parameter_T, estimate.stdyx) %>%
  flextable::flextable() %>%
  flextable::add_header_row(colwidths = c(2), 
                            values = c("Version 2a: Thresholds")) %>%
  flextable::set_header_labels(parameter_T = "Parameter",
                               estimate.stdyx = "Std. Estimate")
```

------------------------------------------------------------------------

# Summary statistics for those where there is a difference in GCP between version 1 and version 2a

-   The recoding mistakes only affected 53 out of 560 participants
-   Mean absolute difference is only 0.02 GCP units

```{r}
sagesI_gcp %>%
  mutate(GCP_v2a_any_diff = GCP_v1 != GCP_v2a,
         GCP_v2a_diff = abs(GCP_v1 - GCP_v2a)) %>%
  filter(GCP_v2a_any_diff == TRUE) %>%
  select(GCP_v2a_diff) %>%
  gtsummary::tbl_summary(
    type = c("GCP_v2a_diff" ~ "continuous2"),
    statistic = gtsummary::all_continuous() ~ c("{N_nonmiss}",
                                                "{mean} ({sd})",
                                     "{median} ({p25}, {p75})", 
                                     "{min}, {max}"),
    label = GCP_v2a_diff ~ "Difference in GCP between v1 and v2a"
  ) %>%
  gtsummary::as_flex_table()


```

------------------------------------------------------------------------

# Fixing the item linking

Animal vs Supermarket naming: Comparison of parameter estimates

```{r}
item_bank_v1 %>%
  filter(item=="Q104") %>%
  filter(parameter_type == "factor_loading") %>%
  select(parameter_T, estimate.stdyx) %>%
  flextable::flextable() %>%
  flextable::add_header_row(colwidths = c(2), 
                            values = c("Version 1: Factor loading")) %>%
  flextable::set_header_labels(parameter_T = "Parameter",
                               estimate.stdyx = "Std. Estimate")

item_bank_v1 %>%
  filter(item=="Q104") %>%
  filter(parameter_type == "threshold") %>%
  select(parameter_T, estimate.stdyx) %>%
  flextable::flextable() %>%
  flextable::add_header_row(colwidths = c(2), 
                            values = c("Version 1: Thresholds")) %>%
  flextable::set_header_labels(parameter_T = "Parameter",
                               estimate.stdyx = "Std. Estimate")

item_bank_v2b %>%
  filter(item=="Q266") %>%
  filter(parameter_type == "factor_loading") %>%
  select(parameter_T, estimate.stdyx) %>%
  flextable::flextable() %>%
  flextable::add_header_row(colwidths = c(2), 
                            values = c("Version 2b: Factor loading")) %>%
  flextable::set_header_labels(parameter_T = "Parameter",
                               estimate.stdyx = "Std. Estimate")

item_bank_v2b %>%
  filter(item=="Q266") %>%
  filter(parameter_type == "threshold") %>%
  select(parameter_T, estimate.stdyx) %>%
  flextable::flextable() %>%
  flextable::add_header_row(colwidths = c(2), 
                            values = c("Version 2b: Thresholds")) %>%
  flextable::set_header_labels(parameter_T = "Parameter",
                               estimate.stdyx = "Std. Estimate")
```

------------------------------------------------------------------------

# Fixing the item linking (Option 1)

FAS : Comparison of parameter estimates

*The threshold parameter estimates are not really comparable, because the Version 1 thresholds are based on bins on number of F+A+S words, and the Version 2b thresholds are based on bins of F, A, and S words considered separately.*

```{r}
item_bank_v1 %>%
  filter(item=="Q117") %>%
  filter(parameter_type == "factor_loading") %>%
  select(parameter_T, estimate.stdyx) %>%
  flextable::flextable() %>%
  flextable::add_header_row(colwidths = c(2), 
                            values = c("Version 1: Factor loading")) %>%
  flextable::set_header_labels(parameter_T = "Parameter",
                               estimate.stdyx = "Std. Estimate")

item_bank_v1 %>%
  filter(item=="Q117") %>%
  filter(parameter_type == "threshold") %>%
  select(parameter_T, estimate.stdyx) %>%
  flextable::flextable() %>%
  flextable::add_header_row(colwidths = c(2), 
                            values = c("Version 1: Thresholds")) %>%
  flextable::set_header_labels(parameter_T = "Parameter",
                               estimate.stdyx = "Std. Estimate")

item_bank_v2b %>%
  filter(item %in% c("Q118", "Q283", "Q284")) %>%
  filter(parameter_type == "factor_loading") %>%
  select(item, parameter_T, estimate.stdyx) %>%
  pivot_wider(names_from = item, values_from = estimate.stdyx) %>%
  flextable::flextable() %>%
  flextable::add_header_row(colwidths = c(4), 
                            values = c("Version 2b: Factor loading")) %>%
  flextable::set_header_labels(parameter_T = "Parameter",
                               Q118 = "F",
                               Q283 = "A",
                               Q284 = "S")

item_bank_v2b %>%
  filter(item %in% c("Q118", "Q283", "Q284")) %>%
  filter(parameter_type == "threshold") %>%
  select(item, parameter_T, estimate.stdyx) %>%
  pivot_wider(names_from = item, values_from = estimate.stdyx) %>%
  flextable::flextable() %>%
  flextable::add_header_row(colwidths = c(4), 
                            values = c("Version 2b: Thresholds")) %>%
  flextable::set_header_labels(parameter_T = "Parameter",
                               Q118 = "F",
                               Q283 = "A",
                               Q284 = "S")
```

------------------------------------------------------------------------

# Summary statistics for those participants where there is a difference between GCP_v1 and GCP_v2b

-   GCP_v1 is not fixing mistakes or item linkages
-   GCP_v2b is fixing the mistakes, animal/supermarket not linked, CFL/FAS as three separate items
-   Fixing the item linkage affects nearly the whole sample
-   The mean absolute difference is 2.2 GCP units

```{r}
sagesI_gcp %>%
  mutate(GCP_v2b_any_diff = GCP_v1 != GCP_v2b,
         GCP_v2b_diff = abs(GCP_v1 - GCP_v2b)) %>%
  filter(GCP_v2b_any_diff == TRUE) %>%
  select(GCP_v2b_diff) %>%
  gtsummary::tbl_summary(
    type = c("GCP_v2b_diff" ~ "continuous2"),
    statistic = gtsummary::all_continuous() ~ c("{N_nonmiss}",
                                                "{mean} ({sd})",
                                     "{median} ({p25}, {p75})", 
                                     "{min}, {max}"),
    label = GCP_v2b_diff ~ "Difference in GCP between v1 and v2b"
  ) %>%
  gtsummary::as_flex_table()


```

# Fixing the item linking (Option 2)

FAS and CFL summed but not linked

FAS : Comparison of parameter estimates

```{r}
item_bank_v1 %>%
  filter(item=="Q117") %>%
  filter(parameter_type == "factor_loading") %>%
  select(parameter_T, estimate.stdyx) %>%
  flextable::flextable() %>%
  flextable::add_header_row(colwidths = c(2), 
                            values = c("Version 1: Factor loading")) %>%
  flextable::set_header_labels(parameter_T = "Parameter",
                               estimate.stdyx = "Std. Estimate")

item_bank_v1 %>%
  filter(item=="Q117") %>%
  filter(parameter_type == "threshold") %>%
  select(parameter_T, estimate.stdyx) %>%
  flextable::flextable() %>%
  flextable::add_header_row(colwidths = c(2), 
                            values = c("Version 1: Thresholds")) %>%
  flextable::set_header_labels(parameter_T = "Parameter",
                               estimate.stdyx = "Std. Estimate")

item_bank_v2c %>%
  filter(item %in% c("Q285")) %>%
  filter(parameter_type == "factor_loading") %>%
  select(parameter_T, estimate.stdyx) %>%
  flextable::flextable() %>%
  flextable::add_header_row(colwidths = c(2), 
                            values = c("Version 2c: Factor loading")) %>%
  flextable::set_header_labels(parameter_T = "Parameter",
                               estimate.stdyx = "Std. Estimate")

item_bank_v2c %>%
  filter(item %in% c("Q285")) %>%
  filter(parameter_type == "threshold") %>%
  select(parameter_T, estimate.stdyx) %>%
  flextable::flextable() %>%
  flextable::add_header_row(colwidths = c(2), 
                            values = c("Version 2c: Thresholds")) %>%
  flextable::set_header_labels(parameter_T = "Parameter",
                               estimate.stdyx = "Std. Estimate")
```

------------------------------------------------------------------------

# Summary statistics for those participants where there is a difference between GCP_v1 and GCP_v2c

-   GCP_v1 is not fixing mistakes or item linkages
-   GCP_v2b is fixing the mistakes, animal/supermarket not linked, CFL/FAS summed but not linked
-   Fixing the item linkage affects nearly the whole sample
-   The mean absolute difference is 1.0 GCP units

```{r}
sagesI_gcp %>%
  mutate(GCP_v2c_any_diff = GCP_v1 != GCP_v2c,
         GCP_v2c_diff = abs(GCP_v1 - GCP_v2c)) %>%
  filter(GCP_v2c_any_diff == TRUE) %>%
  select(GCP_v2c_diff) %>%
  gtsummary::tbl_summary(
    type = c("GCP_v2c_diff" ~ "continuous2"),
    statistic = gtsummary::all_continuous() ~ c("{N_nonmiss}",
                                                "{mean} ({sd})",
                                     "{median} ({p25}, {p75})", 
                                     "{min}, {max}"),
    label = GCP_v2c_diff ~ "Difference in GCP between v1 and v2c"
  ) %>%
  gtsummary::as_flex_table()


```

------------------------------------------------------------------------

# Summary statistics for GCP versions at baseline

```{r}
sagesI_gcp %>%
  select(vdgcp, GCP_v1, GCP_v2a, GCP_v2b, GCP_v2c) %>%
  gtsummary::tbl_summary(type = gtsummary::all_continuous() ~ "continuous2",
    statistic = gtsummary::all_continuous() ~ c("{mean} ({sd})",
                                     "{median} ({p25}, {p75})", 
                                     "{min}, {max}"),
    digits = gtsummary::all_continuous() ~ 2,
    label = vdgcp ~ "Original GCP") %>%
  gtsummary::as_flex_table() 
  
 
```

*Great case to be made for fixing both errors and relaxing both questionable assumptions.*

------------------------------------------------------------------------

# Correlation of GCP versions at baseline

```{r}
sagesI_gcp %>%
  select(vdgcp, GCP_v1, GCP_v2a, GCP_v2b, GCP_v2c) %>%
  cor() %>%
  as_tibble(rownames = NA) %>%
  rownames_to_column() %>%
  rename(variable = rowname) %>%
  flextable::flextable() %>%
  flextable::colformat_double(digits = 2)
  
```

------------------------------------------------------------------------

# Rank order correlation of GCP versions at baseline

```{r}
sagesI_gcp %>%
  select(vdgcp, GCP_v1, GCP_v2a, GCP_v2b, GCP_v2c) %>%
  cor(method = "spearman") %>%
  as_tibble(rownames = NA) %>%
  rownames_to_column() %>%
  rename(variable = rowname) %>%
  flextable::flextable() %>%
  flextable::colformat_double(digits = 2)
  
```

------------------------------------------------------------------------

# Repeating mistakes and item linkages

```{r}
ggplot(sagesI_gcp, aes(x = vdgcp, y = GCP_v1)) +
  geom_point() +
  ggtitle("Original GCP vs New GCP version 1") +
  hrbrthemes::theme_ipsum()
```

------------------------------------------------------------------------

# Fixing the mistakes

```{r}
ggplot(sagesI_gcp, aes(x = vdgcp, y = GCP_v2a)) +
  geom_point() +
  ggtitle("Original GCP vs New GCP version 2a") +
  hrbrthemes::theme_ipsum()
```

------------------------------------------------------------------------

# Fixing mistakes and item linkages (Option 1)

- Animal/Supermarket not linked, CFL/FAS as three separate items

```{r}
ggplot(sagesI_gcp, aes(x = vdgcp, y = GCP_v2b)) +
  geom_point() +
  ggtitle("Original GCP vs New GCP version 2b") +
  hrbrthemes::theme_ipsum()
```

------------------------------------------------------------------------

# Fixing mistakes and item linkages (Option 2)

- Animal/Supermarket not linked, CFL/FAS summed but not linked

```{r}
ggplot(sagesI_gcp, aes(x = vdgcp, y = GCP_v2c)) +
  geom_point() +
  ggtitle("Original GCP vs New GCP version 2c") +
  hrbrthemes::theme_ipsum()
```

------------------------------------------------------------------------

# Absolute difference from original GCP

```{r}
sagesI_gcp %>%
  mutate(diff_v1 = abs(vdgcp - GCP_v1),
         diff_v2a = abs(vdgcp - GCP_v2a),
         diff_v2b = abs(vdgcp - GCP_v2b),
         diff_v2c = abs(vdgcp - GCP_v2c)
         ) %>%
  select(starts_with("diff_")) %>%
  gtsummary::tbl_summary(type = gtsummary::all_continuous() ~ "continuous2",
    statistic = gtsummary::all_continuous() ~ c("{mean} ({sd})",
                                     "{median} ({p25}, {p75})", 
                                     "{min}, {max}"),
    label = c(diff_v1 ~ "abs(Original GCP - V1)",
              diff_v2a ~ "abs(Original GCP - V2a)",
              diff_v2b ~ "abs(Original GCP - V2b)",
              diff_v2c ~ "abs(Original GCP - V2c)")
    ) %>%
  gtsummary::as_flex_table()
```

------------------------------------------------------------------------


```{r, eval=FALSE}
foo <- sagesI_gcp %>%
  left_join(sagesI_npb, by = c("newid" = "newid")) %>%
  mutate(diff_v2a = (GCP_v2a - GCP_v1),
         diff_v2b = (GCP_v2b - GCP_v1)
         ) %>%
  filter(abs(diff_v2b) > 4) %>%
  select(newid, vdgcp, GCP_v1, GCP_v2a, GCP_v2b, diff_v2a, diff_v2b, i282, i283, i284, i265) %>%
  select(-study_name_short, -study_wave_number, -starts_with("g_se"))

foo %>%
  filter(diff_v2b < 0) %>%
  arrange(diff_v2b) %>%
  flextable::flextable()
```
