---
title: "GCP Harmonization Tables & Figures"
author: "Doug Tommet"
date: '`r Sys.Date()`'
format:
  html:
    toc: true
    self-contained: true
    theme: journal
figures:
  fig-cap-location: top 
execute:
  echo: false
  warning: false
  message: false
keep-md: true
---

```{r}
rm(list = setdiff(ls(), lsf.str())[!(setdiff(ls(), lsf.str()) %in% "params")])
source(here::here("R", "001-Libraries_and_functions.R"))
source(here::here("R", "005-folder_paths_and_options.R"))
```

::: callout-note
-   We adapted an in-person cognitive assessment battery for administration by two alternative modes: telephone and videoconference, in an on-going observational study of cognitive aging and delirium

-   We administered all three modes (in-person, telephone, videoconference) in an on-going observational study of older surgical patients.

-   We co-calibrated the scores across mode using item response theory (we placed the scores on the same metric)

-   We compare the measurement precision (reliability) by mode:

-   We contrast the external predictive (and postdictive) validity by mode (association with age, education, and mean change after surgery).
:::

# Differences in GCP from the previous version

There were several different ways we considered harmonizing the test batteries to account for some mistakes and questionable assumptions.

The mistake was when we categorized the test scores into bins, the top two categories were combined into the same bin.

-   Tests this issue affected: VSAT, HVLT total, HVLT delayed and Digit symbol substitution

The questionable assumptions were deciding whether measures of letter fluency and semantic fluency were equivalent. For letter fluency there were three options we considered and for semantic fluency there were two options we considered.

-   Letter fluency:

    -   FAS and FCL summed and deemed equivalent

    -   FAS and FCL as individual tests, F are deemed equivalent, the other letters are not deemed equivalent

    -   FAS and FCL summed but **not** deemed equivalent

-   Semantic fluency:

    -   Animal naming and supermarket item naming are deemed equivalent

    -   Animal naming and supermarket item naming are **not** deemed equivalent

With these as the possible choices, we decided to go with the version that fixes the coding mistakes, FAS/FCL summed but not equivalent and animal/supermarket naming not equivalent.

## @fig-timeline: Timeline of SAGES-I and SAGES-II

```{mermaid}
%%| label: fig-timeline
%%| fig-cap: Timeline of SAGES-I and SAGES-II and the development/roll-out of novel assessment modes
%%| fig-cap-location: top

sequenceDiagram
  participant Before times
  participant After times
  Before times ->>After times: COVID
  Note left of Before times: SAGES II starts enrollment
  Note right of After times: Neuropsych testing procedures updated
```

@fig-timeline is meant to show the development/refinement of the neuropsych testing procedures due to COVID.

::: callout-note
This needs to be sketched out by Eva/Tamara/Field staff.
:::

## @tbl-descriptives: Sample characteristics

```{r}
#| label: tbl-descriptives
#| tbl-cap: Sample characteristics
#| tbl-cap-location: top
sagesII_subject_df_bl <- readRDS(file=path(r_objects_folder, "010_sagesII_subject_df_bl.rds"))

sagesII_subject_df_bl %>%
  select(vdfemale, vdnonwhite, vdeduc_r, vdsurg, vdgds15, vdcci) %>%
  gtsummary::tbl_summary(
    statistic = list(gtsummary::all_continuous() ~ "{mean} ({sd})",
                     gtsummary::all_categorical() ~ "{n} / {N} ({p}%)")
  ) %>%
  gtsummary::modify_caption("SAGES II - Baseline interview")

```

::: callout-note
This is the descriptive statistics for SAGES II at the baseline interview. In the harmonization analysis, for the telephone/video samples the interviews came (mostly) from the follow-up interviews.
:::

## @tbl-battery: Cognitive tests by mode and study

```{r}
#| label: tbl-battery
#| tbl-cap: "Cognitive tests by mode and study"
#| tbl-cap-location: top
 
gcp_items <- readRDS(file=path(r_objects_folder, "010_gcp_items.rds"))
gcp_linking_items <- readRDS(file=path(r_objects_folder, "010_gcp_linking_items.rds")) %>%
  select(item_a, item_b)

gcp_items <- gcp_items %>%
  filter(str_detect(item, "Q")) %>%
  filter(!str_detect(Set, "Not")) %>%
  filter(!str_detect(Set, "DNI")) %>%
  # filter(!str_detect(item, "Q7")) %>%
  left_join(gcp_linking_items, by = c("item" = "item_b")) %>%
  select(item, item_a, item_label, study, domain, Set)

gcp_items_wide <- gcp_items %>%
  mutate(item_new = case_when(!is.na(item_a) ~ item_a,
                              TRUE ~ item),
         x = "X") %>%
  select(item_new, study, x) %>%
  pivot_wider(names_from = study, values_from = x)

gcp_items <- gcp_items_wide %>%
  left_join(gcp_items, by = c("item_new" = "item")) %>%
  select(item_new, item_label, Set, domain, everything()) %>%
  select(-item_a, -study) %>%
  arrange(domain, item_new)

gcp_version <- "GCPv2c"
if (gcp_version == "GCPv1"){
  gcp_alt <- c("GCP-alt-1a", "GCP-alt-2a", "GCP-alt-3a")
}
if (gcp_version == "GCPv2a"){
  gcp_alt <- c("GCP-alt-1b", "GCP-alt-2a", "GCP-alt-3a")
}
if (gcp_version == "GCPv2b"){
  gcp_alt <- c("GCP-alt-1b", "GCP-alt-2b", "GCP-alt-3b")
}
if (gcp_version == "GCPv2c"){
  gcp_alt <- c("GCP-alt-1b", "GCP-alt-2c", "GCP-alt-3b")
}

gcp_items <- gcp_items %>%
  filter(Set %in% c("GCP", gcp_alt))

gcp_items %>%
  gt::gt() %>%
  gt::cols_hide(columns = c(item_new, domain, Set, SAGES_Telephone, INTUIT_ACTIVE, SAGESII_Telephone_validation, SAGESII_Video_validation)) %>%
  gt::cols_align(align = "center") %>%
  gt::tab_row_group(label = "Memory", rows = domain %in% c("mem")) %>%
  gt::tab_row_group(label = "Language", rows = domain %in% c("lan")) %>%
  gt::tab_row_group(label = "Attention/Executive Function", rows = domain %in% c("att", "ef")) %>%
  gt::sub_missing(columns = 3:11, rows = everything(), missing_text = "") %>%
  gt::tab_spanner("Study/Mode", 5:11)
  

```

@tbl-battery shows the neuropsych tests used in the different studys/modes.

## @fig-info: Test Information by mode and study

```{r}
#| label: fig-info
#| fig-cap: "Test Information by mode and study"
#| fig-cap-location: top
gcp_study_nested_v2c <- readRDS(file=path(r_objects_folder, "250_gcp_study_nested_GCPv2c.rds"))

foo <- gcp_study_nested_v2c[["h_obj"]]

foo <- gcp_study_nested_v2c %>%
  mutate(boo = map(h_obj, pluck, "test_info"))

goo <- foo %>%
  select(study_name_short, boo) %>%
  unnest(cols = c(boo))

goo %>%
  filter(study_name_short %in% c("HRS_ADAMS", "SAGES", 
                                 "SAGESII_Inperson", "SAGESII_Telephone", 
                                 "SAGESII_Video")) %>%
  mutate(i = case_when(study_name_short=="SAGES" ~ i + .1,
                       study_name_short=="SAGESII_Video" ~ i - .1,
                       TRUE ~ i)) %>%
ggplot(aes(x = theta, y = i, color = study_name_short)) +
  geom_line() +
  scale_y_continuous("Information") +
  scale_x_continuous("GCP") +
  scale_color_discrete("Study") +
  hrbrthemes::theme_ipsum()

```

@fig-info shows the information plot.

::: callout-note
The cognitive test battery was the same for SAGES I - In-person, SAGES II - In-person, and SAGES II - Video. This means their Information curves would overlap. I shifted the curves by a small amount so they would be distinct.
:::

## @fig-video-vs-telephone: Agreement by mode

```{r}
gcp_g_v2c <- readRDS(file=path(r_objects_folder, "400_gcp_g_v2c.rds"))
validation_df <- gcp_g_v2c %>%
  filter(study_wave_number %in% c(8,9)) %>%
  mutate(id = substr(newid, 3, 9)) %>%
  select(id, gcp, interview_mode) %>%
  pivot_wider(id_cols = id, names_from = interview_mode, values_from = gcp)
```

@tbl-Deming-regression shows the results of Deming regression of telephone and video interview modes.

```{r}
#| label: tbl-Deming-regression
#| tbl-cap: Deming regression results
#| tbl-cap-location: top
# Deming regression
deming_reg <- mcr::mcreg(validation_df$Telephone, validation_df$Video, method.reg = "Deming")
deming_reg@para %>%
  as_tibble() %>%
  select(-SE) %>%
  gt::gt() %>%
  gt::fmt_number(columns = everything(), decimals = 2)
```

```{r}
#| label: fig-video-vs-telephone
#| fig-cap: "Scatterplot of Telephone vs Video GCP in validation sample"
#| fig-cap-location: top

ggplot(validation_df, aes(x=Telephone, y=Video)) +
  geom_point() +
  scale_x_continuous("Telephone GCP", limits = c(40, 90)) +
  scale_y_continuous("Video GCP", limits = c(40, 90)) +
  geom_smooth(se=FALSE, aes(color = "Loess")) +
  geom_abline(slope = 1) +
  geom_abline(aes(slope = deming_reg@para[2], intercept = deming_reg@para[1], 
              color = "Deming")) +
  scale_color_manual("Model", values = c("blue", "red"), breaks = c("Loess", "Deming")) +
  hrbrthemes::theme_ipsum()
```

The correlation of GCP between telephone and video interviews is: `r cor(validation_df$Telephone, validation_df$Video) %>% round(2)`.

```{r}
#| label: fig-bland-altman
#| fig-cap: "Bland-Altman plot of Telephone vs Video GCP in validation sample"
#| fig-cap-location: top

validation_df %>%
  mutate(diff = Telephone-Video,
         avg = (Telephone+Video)/2) %>%
ggplot(aes(x=avg, y=diff)) +
  geom_point() +
  scale_x_continuous("Average between telephone and video") +
  scale_y_continuous("Difference between telephone and video", limits = c(-15, 15)) +
  geom_smooth(se=FALSE) +
  geom_hline(yintercept = 0) +
  hrbrthemes::theme_ipsum()
```

## (Table 3): Validation study results

## @fig-gcp-boxplots: GCP by study

```{r}
#| label: fig-gcp-boxplots
#| fig-cap: GCP by study/mode
#| fig-cap-location: top
gcp_g_v2c %>%
  mutate(study_name_short = factor(study_name_short, 
                                   levels = c("HRS_ADAMS", "SAGES", "SAGESII_Inperson",
                                              "SAGESII_Telephone", "SAGESII_Video",
                                              "SAGESII_Telephone_validation",
                                              "SAGESII_Video_validation", 
                                              "SAGES_Telephone", "INTUIT_ACTIVE"),
                                   labels = c("ADAMS (Unweighted)", "SAGES", "SAGESII - Inperson",
                                              "SAGESII - Telephone", "SAGESII - Video",
                                              "SAGESII - Telephone (validation)", 
                                              "SAGESII - Video (validation)", 
                                              "SAGES - Telephone", "INTUIT/ACTIVE"))) %>%
  filter(!study_wave_number %in% c(7, 6)) %>%
  ggplot(aes(x = gcp, y = study_name_short)) +
  geom_violin() +
  geom_boxplot(width = .25) +
  scale_y_discrete("Study/Mode") +
  scale_x_continuous("GCP") +
  hrbrthemes::theme_ipsum() +
  labs(caption = "Uses all interviews for SAGES & SAGESII modes")


```

::: {.callout-note collapse="true"}
## Expand to see the R session information

```{r} 
sessionInfo()
```
:::
